For finitary induction-Induction, Induction is Enough

### 2020-04-09 paper/paper.tex
cite paper about large inf qiit for morphism between models

Note that initiality refers to a notion of homomorphism between models. As
of now, there is no general metatheory for (large, infinitary) QIITs from which
this notion would be deduced. Hence, we give an ad-hoc definition for
homomorphisms, which can be summarized as a functor between underlying
categories which strictly preserves all additional family structure and type
formers.

>>>>

Here, initiality refers to the notion of homomorphism between models deduced
from the general theory of large infinitary QIITs developed in \cite{large_inf_qiit}.
Roughly, a homomorphism is a functor between underlying
categories which strictly preserves all additional family structure and type
formers.
